\MakeUppercase{Graph Product Structure for Non-Minor-Closed Classes}

### 2022-11-15 k-planar.tex
toned down  response

A \defin{string graph} is the intersection graph of a set of curves (\defin{strings}) in the plane with no three curves meeting at a single point; see  \cite{PachToth-DCG02,FP10,FP14} for example. For an integer $\delta\geq 2$, if each curve is in at most $\delta$ intersections with other curves, then the corresponding string graph is called a \defin{$\delta$-string graph}.\footnote{Every $\delta$-string graph has maximum degree at most $\delta$.  However, it is not necessarily the case that every string graph of maximum degree $\delta$ is a $\delta$-string graph.  If a pair of strings intersect in $c\ge 1$ points, then this counts as $c$ crossings for each string, but only contributes one to the degree of each.} A \defin{$(g,\delta)$-string} graph is defined analogously for curves on a surface of Euler genus at most $g$.

>>>>

A \defin{string graph} is the intersection graph of a set of curves (\defin{strings}) in the plane with no three curves meeting at a single point; see  \cite{PachToth-DCG02,FP10,FP14} for example. For an integer $\delta\geq 2$, if each curve is in at most $\delta$ intersections with other curves, then the corresponding string graph is called a \defin{$\delta$-string graph}.\footnote{Every $\delta$-string graph has maximum degree at most $\delta$.  However, it is not necessarily the case that every string graph of maximum degree $\delta$ is a $\delta$-string graph.  If a pair of strings intersect in $c\ge 1$ points, then this counts as $c$ crossings for each string, but only contributes one to their degree.} A \defin{$(g,\delta)$-string} graph is defined analogously for curves on a surface of Euler genus at most $g$.

### 2022-11-15 response2.tex
toned down  response

\begin{response}
  We have added the qualifier "bounded-degree" here, even though the $\delta$-string condition is actually stronger.  (A pair of strings may cross more than once, in which case each of these crossings counts against $\delta$.)   At this point in the introduction (not yet having defined a string graph), this is hopefully a good enough approximation.  The first paragraph of Section 3.1 gives the definition of $\delta$-string graph and makes note of the distinction between $\delta$-string graph and string graph of maximum degree at most $\delta$.  Hopefully anyone that wants to make use of Theorem~14 will read the definition of $\delta$-string graph.
\end{response}

>>>>

\begin{response}
  We have added the qualifier "bounded-degree" here, although the $\delta$-string condition is actually stronger.  (A pair of strings may cross more than once, in which case each of these crossings counts against $\delta$.)   At this point in the introduction (not yet having defined a string graph), this is hopefully a good enough approximation.  The first paragraph of Section 3.1 gives the definition of $\delta$-string graph and makes note of the distinction between $\delta$-string graph and string graph of maximum degree at most $\delta$.  
  %Hopefully anyone that wants to make use of Theorem~14 will read the definition of $\delta$-string graph. DW: This could be deemed an attack on the referee. 
\end{response}
